An Automatic Verification Framework for Software Configurations

### 2016-05-10 OSDI/trans.tex
update trans

In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
If $t(v1, v2)$ holds, \ie the template condition is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.

With the help of probabilistic types, we addressed ambiguities during the parsing phase. Another problem that we need to solve
is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
sets conditions under which some action should be applied. Therefore, we also add this guard to our entry 
during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.

To summarize, the translator translates every entry ${\tt {k = v}}$ in a configuration file into a quadruple 
$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$

>>>>

In general, the templates works as follows: if there are two entries ${\tt {k1 = v1}}$ and 
${\tt {k2 = v2}}$, let $t(X, Y)$ be a template that can be applied to those values (w.r.t. their types).
If $t(v1, v2)$ holds, \ie, the template condition is valid for those concrete values, then we will add a rule
$t(k1, k2)$ to a list of potentially correct specifications. Note that the rule expresses a relation between variables.

With the help of probabilistic types, we addressed ambiguities during the parsing phase. Another problem that we need to solve
is that configuration files sometimes contain a simple version of the {\tt {if-then}}, such as in Apache HTTPD, that 
sets conditions for which an action should be applied. Therefore, we also add this guard to our entry 
during the parsing phase. We first check if the guard is true before deriving a rule; otherwise, we skip the entry.

To summarize, the translator translates every entity ${\tt {k = v}}$ in a configuration file into a quadruple entry
$$(g,k,v,\textsf{List}[p_1:\tau_1, \ldots, p_n:\tau_n])$$
